Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-21 awipev-CO2.Rmd
- added date in discrete df - calculate mean at ct per date rather than per datetime...

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
#d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
d$datetime <- dmy_hm(d$sampling_date, tz="UTC")
d$measure_date <- dmy(d$measure_date, tz="UTC")

@@

# Mercuric chloride correction (Dickson et al. 2007, SOP3a)
# AT
d$at <- d$at * 1.0002
#CT
d$ct <- d$ct * 1.0002

@@

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH = pH_seafet$pH_s_seafet,ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))

@@

# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,ph_s_sf_temp_mix)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_sf_temp_mix = mean(ph_s_sf_temp_mix, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,ph_s_dur_temp_fb)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = T))

@@

carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6,S=discrete_no_na$sal_fb, T=discrete_no_na$temp_fb, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")

@@

### **Calculated / Durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal_fb,temp_fb, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp_fb), !is.na(sal_fb))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

>>>>

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
#d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
d$datetime <- dmy_hm(d$sampling_date, tz="UTC")
d$measure_date <- dmy(d$measure_date, tz="UTC")
d$date <- as.Date(d$datetime)

@@

# Mercuric chloride correction (Dickson et al. 2007, SOP3a)
d$at <- d$at * 1.0002
d$ct <- d$ct * 1.0002

@@

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH = pH_seafet$pH_s_seafet, ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))

@@

# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime, ph_s_sf_temp_mix)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_sf_temp_mix = mean(ph_s_sf_temp_mix, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime, ph_s_dur_temp_fb)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = T))

@@

carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")

@@

### **Calculated / Durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal_fb, temp_fb, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp_fb), !is.na(sal_fb))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
